### 2018-05-14 tex/paper.tex
Add embedded Marlowe explanation to paper

In this section, we revisit the escrow example that we discussed briefly in the introduction, and show  how we can make Marlowe contracts that are easier to write, read, and 
understand, by embedding them into Haskell code, taking advantage of the fact that Marlowe contracts are implemented as Haskell 
terms.

@@

One of the objectives of Marlowe is to be accessible to a wider audience
than a general purpose language would. With this aim, and to aid Marlowe's
usage by people that does not know is not familiar with its syntax,
we have developed Meadow, a web tool that supports the interactive construction,
edition, and simulation of smart-contracts written in Marlowe. The
tool is publicly available in the url: \url{https://input-output-hk.github.io/scdsl/}.
In Figure~\ref{fig:full-screenshot-demo}, we provide a screenshot
of Meadow in the middle of simulating the execution of the ``incentivised
saving'' contract described in Section~\ref{section:example-saving}.

Meadow has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler~\cite{Haste}, it also relies on
the Blockly library~\cite{Blockly} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). Meadow also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

@@

In the next section we re-examine the model and the Marlowe language, looking at possible extensions, alternative design decisions and ways in which we can formally analyse Marlowe contracts.

>>>>

In this section, we revisit the escrow example that we discussed briefly in the introduction, and show how we can make 
Marlowe contracts that are easier to write, read, and understand, by embedding them into Haskell code, taking advantage 
of the fact that Marlowe contracts are implemented as Haskell terms. We used Haskell because it is the language in 
which Marlowe is implemented, but it would be easy to embed Marlowe in any other languages. It would only be necessary 
to translate its primitives into a data type in that language. In Meadow, we use Fay embedding, which is a subset of 
Haskell (see Section~\ref{section:tool}).

@@

One of the objectives of Marlowe is to be accessible to a wider audience
than a general purpose language would. With this aim, and to aid Marlowe's
usage by people that does not know or is not familiar with its syntax,
we have developed Meadow, a web tool that supports the interactive construction,
edition, and simulation of smart-contracts written in Marlowe. The
tool is publicly available in the url: \url{https://input-output-hk.github.io/scdsl/}.
In Figure~\ref{fig:full-screenshot-demo}, we provide a screenshot
of Meadow in the middle of simulating the execution of the ``incentivised
saving'' contract described in Section~\ref{section:example-saving}.

Meadow has been mainly written in Haskell and compiled to JavaScript
partially by the Haste compiler~\cite{Haste} and partially by GHCJS \cite{GHCJS};
Meadow also relies on the Blockly library~\cite{Blockly} for providing a visual
editor for smart contracts written in Marlowe. Embedding support in Meadow
is provided throught a pruned and bundled version of the Fay compiler \cite{Fay},
compiled to JavaScript using GHCJS. All text fields that edit and present Meadow and Fay code are
instances of CodeMirror text editor \cite{CodeMirror}.

Blockly's editor allows the user to visualise and edit
smart-contracts as interlocking blocks that can be dragged and dropped
like pieces of a jigsaw puzzle (see Figure~\ref{fig:detail-of-block}).
Meadow also provides functionality to generate syntactically correct
and formatted code (that is displayed in the upper right corner of the application),
and to convert the code back to its block representation.

Additionally, Meadow allows the user to use Meadow's Fay embedding from within the browser (see 
Figure~\ref{fig:embedded-demo}). Meadow includes a pruned copy of the Fay compiler, bundled with its Prelude module, 
its foreign interface, and a module with the definitions of the Marlowe primitives and a function to pretty-print 
Marlowe contracts. This allows the user to compile and execute, inside the browser, Fay
code that generates and prints a Meadow contract. When the user opens the embedded editor, the current Marlowe contract 
is embedded into a template of a Fay program that prints it. The user is able to modify this code in the left 
panel of the editor and use the advanced functionalities provided by Fay like, for example, bindings, 
list-comprehensions, turing-complete functions definitions, etc.

When the user clicks the execute button, the Fay code is 
compiled to JavaScript and evaluated; this causes the Marlowe contract generated by the execution of the code to be 
written to the panel on the right. Generated contracts can then be sent back to the main screen of Meadow, translated 
to Blockly, and their execution can be simulated. The embedded editor also allows users to save the Fay code to a 
file in their computers, to load code from a file in their computers, and to temporarily hide the editor while keeping 
its contents in memory, even while the compilation and execution process is being carried out in the background.

@@

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{/home/palas/Escritorio/scdsl/tex/pix/embedded.png}
\par\end{centering}
\caption{\label{fig:embedded-demo}Screenshot of Meadow's embedded Fay editor.}
\end{figure}

In the next section, we re-examine the model and the Marlowe language, looking at possible extensions, alternative 
design decisions and ways in which we can formally analyse Marlowe contracts.
